---
title: "Taxo Cleaner"
---


#Lines having to be adapted to data
###Desired n° of candidates 
```{r}
top_candidates <- 500000
```

###Inputs
```{r}
#Path to ISDB result
input_ISDB_path <- "https://osf.io/yunm8/download"

#Path to MSFinder result
input_MSFinder_path <- "https://osf.io/2h7y9/download"

#Path to Sirius result
input_Sirius_path <- "https://osf.io/57tw6/download"

#Path to metadata with structures/biosources information
Metadata_path <- ""

#Path to GNPS file containing Spectrum ID
Spectrum_ID_file_path <- "https://osf.io/un8ey/download"

#Only for the standards
input_STDS_path <- "https://osf.io/ye4gx/download"
```

###Outputs
```{r}
#Path to curated result of ISDB
output_ISDB_path <- "~/Data/Curated/ISDB_DNP_output_curated.tsv"

#Path to curated result of MSFinder
output_MSFinder_path <- "~/Data/Curated/MS_Finder_output_curated.tsv"

#Path to curated result of Sirius
output_Sirius_path <- "~/Data/Curated/Sirius_output_curated.tsv"

#Path to curated standards
output_STDS_path <- "~/Data/Curated/benchmarking_dataset_metadata_curated.tsv"
```

#Requested packages
```{r}
library(data.table)
library(feather)
library(readr)
library(dplyr)
library(splitstackshape)
library(stringr)
```

Outputing packages versions
```{r}
packageVersion('data.table')
packageVersion('feather')
packageVersion('readr')
packageVersion('dplyr')
packageVersion('splitstackshape')
packageVersion('stringr')
```

Loading the output files, standard file, and metadata file
```{r}
ISDBout <- read_delim(input_ISDB_path, "\t", escape_double = FALSE, trim_ws = TRUE)

MSFinderout <- read_delim(input_MSFinder_path, "\t", escape_double = FALSE, trim_ws = TRUE)

Siriusout <- read_delim(input_Sirius_path, "\t", escape_double = FALSE, trim_ws = TRUE)

STDS_tax <- read_delim(input_STDS_path, "\t", escape_double = FALSE, trim_ws = TRUE)

Metadata <- read_delim(Metadata_path, "\t", escape_double = FALSE, trim_ws = TRUE)

Spectrum_ID_file <- read_delim(Spectrum_ID_file_path, "\t", escape_double = FALSE, trim_ws = TRUE)
```

# Preliminary cleaning
###ISDB
Adding Spectrum ID
```{r}
Spectrum_ID_file$observation <- 1:nrow(Spectrum_ID_file)

Spectrum_ID_file <- Spectrum_ID_file %>%
  select(observation, spectrum_id_val)

ISDBout = left_join(ISDBout, Spectrum_ID_file, by = c("cluster index" = "observation"), match = "all")
```

Keeping required columns
```{r}
ISDBout <- ISDBout %>% 
  select(spectrum_id_val, InChIKey_DNP, Spectral_Score_DNP)
```

Splitting columns
```{r}
ISDBout <- ISDBout %>%
  as.data.table() %>%
  cSplit("InChIKey_DNP", "|") %>%
  cSplit("Spectral_Score_DNP", "|")
```

Melting the data
```{r}
ISDBout_melted <- melt(setDT(ISDBout), id = ,
                       measure = patterns("^InChIKey_DNP",
                                          "^Spectral_Score_DNP"), 
                       value.name = c("InChIKey_DNP", 
                                      "Spectral_Score_DNP"),
                       variable.name = "Rank")
```

Removing unnecessary columns
```{r}
ISDBout_cleaned <- ISDBout %>%
  select(-contains("DNP_"))
```

Adding Cluster Index
```{r}
ISDBout_merged = left_join(ISDBout_cleaned, ISDBout_melted)
```

Generating ShortIK
```{r}
tempIK <- str_split_fixed(ISDBout_merged$InChIKey_DNP, "-", 3)

ISDBout_merged$"Short_IK_ISDB" = tempIK[,1]
```

###MSFinder
Melting the data
```{r}
MSFinderout_melted <- melt(setDT(MSFinderout), id = ,
                           measure = patterns("^Structure rank",
                                              "^Total score",
                                              "^Databases",
                                              "^Ontology",
                                              "^InChIKey",
                                              "^Formula",
                                              "^SMILES"),
                           value.name = c("Structure rank",
                                          "Total score",
                                          "Databases",
                                          "Ontology",
                                          "InChIKey",
                                          "Formula",
                                          "SMILES"),
                           variable.name = "Rank")
```

Keeping required columns
```{r}
MSFinderout_melted <- MSFinderout_melted %>% 
  select(Title, Rank, 'Total score', InChIKey)
```

Getting proper short IK
```{r}
MSFinderout_melted$Short_IK <- substr(MSFinderout_melted$InChIKey, 0, 14)
```

###Sirius  
Cleaning of useless columns
```{r}
Siriusout <- Siriusout%>%
  filter(str_detect(inchi, "^InChI"))
```

Renaming column
```{r}
colnames(Siriusout)[1]<-"inchikey2D"
```

Splitting columns to get proper short IK
```{r}
Siriusout <- Siriusout %>%
  cSplit("inchikey2D", ":")%>%
  cSplit("inchikey2D_1", ".")
```


```{r}
Siriusout <- Siriusout%>%
  select(inchikey2D_1_1, inchikey2D_2, rank, score)
```

```{r}
sirius_unique <- Siriusout[!duplicated(Siriusout$inchikey2D_1_1),]
```

###Metadata
```{r}
Metadata_cleaned <- Metadata %>% 
  select(Short_IK_DNP, Kingdom, Phylum, Class, Order, Family, Genus, Species, Subspecies, Kingdom_cf, Superclass_cf, Class_cf, Subclass_cf, Parent_Level_1_cf, Parent_Level_2_cf, Parent_Level_3_cf, Parent_Level_4_cf, Parent_Level_5_cf, Parent_Level_6_cf, Accurate_Mass)
```

###STDS
Renaming columns
```{r}
colnames(STDS_tax) <- paste(colnames(STDS_tax), "STDS", sep = "_")
colnames(STDS_tax)[7]<-"ID_STDS"
```

```{r}
STDS_cleaned <- STDS_tax %>% 
  select(ID_STDS, Short_IK_STDS, Kingdom_STDS, Phylum_STDS, Class_STDS, Order_STDS, Family_STDS, Genus_STDS, Species_STDS, Subspecies_STDS, Kingdom_cf_STDS, Superclass_cf_STDS, Class_cf_STDS, Subclass_cf_STDS, Parent_Level_1_cf_STDS, Parent_Level_2_cf_STDS, Parent_Level_3_cf_STDS, Parent_Level_4_cf_STDS, Parent_Level_5_cf_STDS, Parent_Level_6_cf_STDS, Accurate_Mass_STDS, pepmass_val_STDS, sourceinstr_val_STDS, lib_val_STDS)
```

###Harmonizing outputs
```{r}
Siriusout <- Siriusout%>%
  mutate_at(vars(matches("rank")),list(as.numeric))%>%
  select(ID_query = inchikey2D_1_1, Short_IK_query = inchikey2D_2, Rank_query = rank, Score_query = score)%>%
  mutate(Score_query = as.numeric(Score_query))%>%
  mutate(Short_IK_query = as.character(Short_IK_query))%>%
  mutate(ID_query = as.character(ID_query))%>%
  data.table()

MSFinderout <- MSFinderout_melted%>%
  mutate_at(vars(matches("Rank")),list(as.numeric))%>%
  select(ID_query = Title, Short_IK_query = Short_IK, Rank_query = Rank, Score_query =`Total score`)%>%
  data.table()
MSFinderout <- MSFinderout[MSFinderout$Short_IK_query != '',]

ISDBout <- ISDBout_merged%>%
  mutate_at(vars(matches("Rank")),list(as.numeric))%>%
  select(ID_query = spectrum_id_val, Short_IK_query = Short_IK_ISDB, Rank_query = Rank, Score_query = Spectral_Score_DNP) %>%
  data.table()
ISDBout <- ISDBout[ISDBout$Short_IK_query != '',]
```

Keeping only the desired candidates
```{r}
Siriusout_top <- filter(Siriusout, Rank_query <= top_candidates)
MSFinderout_top <- filter(MSFinderout, Rank_query <= top_candidates)
ISDBout_top <- filter(ISDBout, Rank_query <= top_candidates)
```

#Adding metadata
```{r}
Siriusout_merged_taxed = left_join(Siriusout_top, Metadata_cleaned, by = c("Short_IK_query" = "Short_IK_DNP"), match = "all")

MSFinderout_merged_taxed = left_join(MSFinderout_top, Metadata_cleaned, by = c("Short_IK_query" = "Short_IK_DNP"), match = "all")

ISDBout_merged_taxed = left_join(ISDBout_top, Metadata_cleaned, by = c("Short_IK_query" = "Short_IK_DNP"), match = "all")
```

#Merging with standards
Merging files by unique ID
```{r}
Siriusout_tax_STDS = left_join(Siriusout_merged_taxed, STDS_cleaned, by = c("ID_query" = "ID_STDS"), match = "all")

MSFinderout_tax_STDS = left_join(MSFinderout_merged_taxed, STDS_cleaned, by = c("ID_query" = "ID_STDS"), match = "all")

ISDBout_tax_STDS = left_join(ISDBout_merged_taxed, STDS_cleaned, by = c("ID_query" = "ID_STDS"), match = "all")
```

Matching with the standards to get the correct hits
```{r}
Siriusout_tax_STDS$MatchVal <- ifelse(Siriusout_tax_STDS$Short_IK_query == Siriusout_tax_STDS$Short_IK_STDS, "Match", "NoMatch")

MSFinderout_tax_STDS$MatchVal <- ifelse(MSFinderout_tax_STDS$Short_IK_query == MSFinderout_tax_STDS$Short_IK_STDS, "Match", "NoMatch")

ISDBout_tax_STDS$MatchVal <- ifelse(ISDBout_tax_STDS$Short_IK_query == ISDBout_tax_STDS$Short_IK_STDS, "Match", "NoMatch")
```

#Exporting
```{r}
write_csv(Siriusout_tax_STDS, output_Sirius_path)
write_csv(MSFinderout_tax_STDS, output_MSFinder_path)
write_csv(ISDBout_tax_STDS, output_ISDB_path)
write_csv(STDS_cleaned, output_STDS_path)
```