---
title: "TaxoDesigneR"
---

#Requested Files 
```{r}
#Input here weighed annotation result of ISDB
input_weighed_ISDB_path <- "../Data/Weighted/ISDB_weighted.tsv"

#Input here weighed annotation result of MSFinder
input_weighed_MSFinder_path <- "../Data/Weighted/MSFinder_weighted.tsv"

#Input here weighed annotation result of Sirius
input_weighed_Sirius_path <- "../Data/Weighted/Sirius_weighted.tsv"

#F1 scores
input_f1_scores_path <- "../Data/Weighted/F1_scores.tsv"

#Only for the standards
input_cleaned_STDS_path <- "../Data/Curated/STDS_cleaned.tsv"

#DNP
input <- "~/190602_DNP_TAXcof_CF.tsv"
```

#Requested Packages
```{r}
library(data.table)
library(dplyr)
library(eulerr)
library(feather)
library(plotly)
library(readr)
library(viridis)
library(ggmosaic)
library(RColorBrewer)
library(htmlwidgets)
```

Loading the files obtained after cleaning
```{r}
ISDBout_weighted <- read_feather(
  input_weighed_ISDB_path
  )

MSFinderout_weighted <- read_feather(
  input_weighed_MSFinder_path
  )

Siriusout_weighted <- read_feather(
  input_weighed_Sirius_path
  )

F1_scores <- read_feather(
  input_f1_scores_path
  )

STDS_tax <- read_feather(
  input_cleaned_STDS_path
  )

File <- read_delim(
  file = input,
  delim = "\t", 
  escape_double = FALSE,
  trim_ws = TRUE
  ) 

col_seq_12 <- brewer.pal(12, "Paired")
```

#Global Results
Merging all results
```{r}
# we add a suffix to differentiate outputs

ISDBout_tomerge <- ISDBout_weighted
Siriusout_tomerge <- Siriusout_weighted 
MSFinderout_tomerge <- MSFinderout_weighted 

# we add a suffix to differentiate outputs

colnames(ISDBout_tomerge) <- paste(colnames(ISDBout_tomerge), "ISDB", sep = "_")
colnames(Siriusout_tomerge) <- paste(colnames(Siriusout_tomerge), "Sirius", sep = "_")
colnames(MSFinderout_tomerge) <- paste(colnames(MSFinderout_tomerge), "MSFinder", sep = "_")

# rename unique ids

STDS_tax <- STDS_tax %>% 
  mutate(ID_query = ID_STDS)
ISDBout_tomerge <- ISDBout_tomerge %>% 
  mutate(ID_query = ID_query_ISDB)
Siriusout_tomerge <- Siriusout_tomerge %>% 
  mutate(ID_query = ID_query_Sirius)
MSFinderout_tomerge <- MSFinderout_tomerge %>% 
  mutate(ID_query = ID_query_MSFinder)

# and merge

Global_Taxo <- left_join(STDS_tax, ISDBout_tomerge, by = "ID_query", all = TRUE)
Global_Taxo <- left_join(Global_Taxo, Siriusout_tomerge, by = "ID_query", all = TRUE)
Global_Taxo <- left_join(Global_Taxo, MSFinderout_tomerge, by = "ID_query", all = TRUE)
```

##Identified
```{r}
Identified <- Global_Taxo %>% 
  filter(
    ID_query == ID_query_Sirius | ID_query == ID_query_MSFinder | ID_query ==ID_query_ISDB
    ) 
```

##Non-Identified
```{r}
Non_Identified <- anti_join(
  STDS_tax,
  Identified
  )
```

##Biological Families
```{r}
Names_List_Families <- (unique(STDS_tax$Family_STDS))

Counts_List_Families <- (unique(STDS_tax$Family_STDS))
for(i in seq_along(Counts_List_Families)){Counts_List_Families[[i]] <- nrow(subset(STDS_tax, Family_STDS == Names_List_Families[[i]]))}

Found_List_Families <- (unique(STDS_tax$Family_STDS))
for(i in seq_along(Found_List_Families)){Found_List_Families[[i]] <- nrow(subset(Identified, Family_STDS == Names_List_Families[[i]]))}

Missing_List_Families <- (unique(STDS_tax$Family_STDS))
for(i in seq_along(Missing_List_Families)){Missing_List_Families[[i]] <- nrow(subset(Non_Identified,Family_STDS == Names_List_Families[[i]]))}

Plotting_Families <- data.frame(Names_List_Families, as.numeric(Counts_List_Families), as.numeric(Found_List_Families), as.numeric(Missing_List_Families))

Plotting_Families <- na.omit(mutate(Plotting_Families, Families_found_percent = round(100 * as.numeric.Found_List_Families. / as.numeric.Counts_List_Families., digits = 1), Families_not_found_percent = round(100 * as.numeric.Missing_List_Families. / as.numeric.Counts_List_Families., digits = 1)))

Plotting_Families$Names_List_Families <- factor(Plotting_Families$Names_List_Families, levels = unique(Plotting_Families$Names_List_Families)[order(Plotting_Families$as.numeric.Counts_List_Families., decreasing = TRUE)])
```

```{r}
Plotting_Families_2 <- Plotting_Families %>% 
  filter(as.numeric.Counts_List_Families. >= 15)

Plotting_Families_2$Names_List_Families <- factor(Plotting_Families_2$Names_List_Families, levels = unique(Plotting_Families_2$Names_List_Families)[order(Plotting_Families_2$as.numeric.Counts_List_Families., decreasing = TRUE)])

File3 <- File %>% 
  select(Kingdom_cof_DNP, Phylum_cof_DNP, Class_cof_DNP, Order_cof_DNP, Family_cof_DNP, Genus_cof_DNP, Species_cof_DNP)

Plotting_Families_2$Names_List_Families <- as.character(Plotting_Families_2$Names_List_Families)

Plotting_Families_3 <- left_join(
  Plotting_Families_2, 
  File3,
  by = c(Names_List_Families = "Family_cof_DNP")
  )

Plotting_Families_3 <- Plotting_Families_3 %>% 
  distinct(Names_List_Families, .keep_all = TRUE)

Plotting_Families_3$Names_List_Families <- factor(Plotting_Families_3$Names_List_Families, levels = unique(Plotting_Families_3$Names_List_Families)[order(Plotting_Families_3$as.numeric.Counts_List_Families., decreasing = TRUE)])
```

##Mass densities
```{r}
File2 <- File %>% 
  distinct(CRC_Number_DNP, .keep_all = TRUE) %>% 
  filter(!is.na(Accurate_Mass_DNP))

Global_Taxo2 <- Global_Taxo %>% 
  filter(!is.na(Accurate_Mass_STDS))
```

```{r}
density1 <- density(File2$Accurate_Mass_DNP)

density2 <- density(Global_Taxo2$Accurate_Mass_STDS)
```

##Chemical diversity
```{r}
Count_Classes_cf <- Global_Taxo %>%
 count(Class_cf_STDS, sort = TRUE) %>% 
  mutate(Percent = 100* n / sum(n))
```

```{r}
Classes_cf4pie <- Count_Classes_cf %>%
  mutate(Class_cf_STDS = if_else(Percent < 1, "Less than 1%", Class_cf_STDS)) %>% 
  filter(!is.na(Class_cf_STDS)) %>% 
  group_by(Class_cf_STDS) %>% 
  summarise_all(sum) %>% 
  ungroup()
```

```{r}
Count_Classes_DNP_cf <- File2 %>%
 count(Class_cf_DNP, sort = TRUE) %>% 
  mutate(Percent = 100* n / sum(n))
```

```{r}
Classes_DNP_cf4pie <- Count_Classes_DNP_cf %>%
  mutate(Class_cf_DNP = if_else(Percent < 1, "Less than 1%", Class_cf_DNP)) %>% 
  filter(!is.na(Class_cf_DNP)) %>% 
  group_by(Class_cf_DNP) %>% 
  summarise_all(sum) %>% 
  ungroup()
```

##MS instrument
```{r}
STDS_sourceinstr <- STDS_tax %>%
  count(
    sourceinstr_val_STDS,
    sort = TRUE
    )

STDS_sourceinstr$QTOF = ifelse(grepl(pattern = "TOF|impact", x = STDS_sourceinstr$sourceinstr_val_STDS, ignore.case = T), STDS_sourceinstr$n, 0)
STDS_sourceinstr$FT = ifelse(grepl(pattern = "FT|exactive|orbitrap", x = STDS_sourceinstr$sourceinstr_val_STDS, ignore.case = T), STDS_sourceinstr$n, 0)
STDS_sourceinstr$IT = ifelse(grepl(pattern = "-IT$|ion trap", x = STDS_sourceinstr$sourceinstr_val_STDS, ignore.case = T), STDS_sourceinstr$n, 0)
STDS_sourceinstr$QQQ = ifelse(grepl(pattern = "QQ", x = STDS_sourceinstr$sourceinstr_val_STDS, ignore.case = T), STDS_sourceinstr$n, 0)

STDS_tax$MS_source_type <- STDS_tax$sourceinstr_val_STDS

STDS_tax$MS_source_type = ifelse(grepl(pattern = "TOF|impact", x = STDS_tax$sourceinstr_val_STDS, ignore.case = T), 'TOF', STDS_tax$MS_source_type)
STDS_tax$MS_source_type = ifelse(grepl(pattern = "FT|exactive|orbitrap", x = STDS_tax$sourceinstr_val_STDS, ignore.case = T), 'FT', STDS_tax$MS_source_type)
STDS_tax$MS_source_type = ifelse(grepl(pattern = "-IT$|ion trap", x = STDS_tax$sourceinstr_val_STDS, ignore.case = T), 'IT', STDS_tax$MS_source_type)
STDS_tax$MS_source_type = ifelse(grepl(pattern = "QQ", x = STDS_tax$sourceinstr_val_STDS, ignore.case = T), 'QQQ', STDS_tax$MS_source_type)
```

##Venn
###initial
```{r}
Venn_initial = c(
"Sirius_initial" = nrow(subset(Global_Taxo, 
                       Global_Taxo$RANK_BEFORE_Sirius == 1)),
"MSFinder_initial" = nrow(subset(Global_Taxo, 
                         Global_Taxo$RANK_BEFORE_MSFinder == 1)),
"ISDB_initial" = nrow(subset(Global_Taxo, 
                     Global_Taxo$RANK_BEFORE_ISDB == 1)),
"Sirius_initial&MSFinder_initial" = nrow(subset(Global_Taxo, 
                                Global_Taxo$RANK_BEFORE_Sirius == 1 & 
                                Global_Taxo$RANK_BEFORE_MSFinder == 1)),
"MSFinder_initial&ISDB_initial" = nrow(subset(Global_Taxo,
                              Global_Taxo$RANK_BEFORE_MSFinder == 1 & 
                              Global_Taxo$RANK_BEFORE_ISDB == 1)),
"Sirius_initial&ISDB_initial" = nrow(subset(Global_Taxo, 
                            Global_Taxo$RANK_BEFORE_Sirius == 1 & 
                            Global_Taxo$RANK_BEFORE_ISDB == 1)),
"Sirius_initial&MSFinder_initial&ISDB_initial" = nrow(subset(Global_Taxo, 
                                     Global_Taxo$RANK_BEFORE_Sirius == 1 & 
                                     Global_Taxo$RANK_BEFORE_MSFinder == 1 &
                                     Global_Taxo$RANK_BEFORE_ISDB == 1))
)
```

###weighted
```{r}
Venn = c(
"Sirius" = nrow(subset(Global_Taxo, Global_Taxo$RANK_FINAL_Sirius == 1)),
"MSFinder" = nrow(subset(Global_Taxo, Global_Taxo$RANK_FINAL_MSFinder == 1)),
"ISDB" = nrow(subset(Global_Taxo, Global_Taxo$RANK_FINAL_ISDB == 1)),
"Sirius&MSFinder" = nrow(subset(Global_Taxo, Global_Taxo$RANK_FINAL_Sirius == 1 & Global_Taxo$RANK_FINAL_MSFinder == 1)),
"MSFinder&ISDB" = nrow(subset(Global_Taxo, Global_Taxo$RANK_FINAL_MSFinder == 1 & Global_Taxo$RANK_FINAL_ISDB == 1)),
"Sirius&ISDB" = nrow(subset(Global_Taxo, Global_Taxo$RANK_FINAL_Sirius == 1 & Global_Taxo$RANK_FINAL_ISDB == 1)),
"Sirius&MSFinder&ISDB" = nrow(subset(Global_Taxo, Global_Taxo$RANK_FINAL_Sirius == 1 & Global_Taxo$RANK_FINAL_MSFinder == 1 & Global_Taxo$RANK_FINAL_ISDB == 1))
)
```

##ROC
```{r}
ISDB <- 1:500
for(i in seq_along(ISDB)){ISDB[[i]] <- c(nrow(subset(ISDBout_tomerge, RANK_BEFORE_ISDB <= i)))}
Sirius <- 1:500
for(i in seq_along(Sirius)){Sirius[[i]] <- c(nrow(subset(Siriusout_tomerge, RANK_BEFORE_Sirius <= i)))}
MSFinder <- 1:500
for(i in seq_along(MSFinder)){MSFinder[[i]] <- c(nrow(subset(MSFinderout_tomerge, RANK_BEFORE_MSFinder <= i)))}
ISDB_Weighted <- 1:500
for(i in seq_along(ISDB_Weighted)){ISDB_Weighted[[i]] <- c(nrow(subset(ISDBout_tomerge, RANK_FINAL_ISDB <= i)))}
Sirius_Weighted <- 1:500
for(i in seq_along(Sirius_Weighted)){Sirius_Weighted[[i]] <- c(nrow(subset(Siriusout_tomerge, RANK_FINAL_Sirius <= i)))}
MSFinder_Weighted <- 1:500
for(i in seq_along(MSFinder_Weighted)){MSFinder_Weighted[[i]] <- c(nrow(subset(MSFinderout_tomerge, RANK_FINAL_MSFinder <= i)))}

ROC <- data.frame(ISDB, Sirius, MSFinder, ISDB_Weighted, Sirius_Weighted, MSFinder_Weighted)
ROC <- rbind(c(0, 0, 0, 0, 0, 0), ROC)
ROC$x <- 0:500
ROC[1,7] <- 1
```

#Plotting
##Setting fonts
```{r}
l <- list(
  font = list(
    family = "Helvetica",
    size = 24,
    color = '#000000',
    bgcolor = "#34495E",
    bordercolor = "#34495E",
    borderwidth = 2))
l2 <- list(
  font = list(
    family = "Helvetica",
    size = 32,
    color = '#000000',
    bgcolor = "#34495E",
    bordercolor = "#34495E",
    borderwidth = 2),
  x = 51,
  y = 0.85)
f <- list(
  family = "Helvetica",
  size = 24,
  color = '#000000')

w <- list(
  family = "Helvetica",
  size = 24,
  color = '#FFFFFF')

f2 <- list(
  family = "Helvetica",
  weight = "bold",
  size = 32,
  color = '#000000')

m <- list(
  l = 0,
  r = 0,
  b = 0,
  t = 0,
  pad = 10
)
```

##Set vs DNP Masses density
```{r}
dens_plot <- plot_ly(
  x = ~density1$x,
  y = ~density1$y,
  type = 'scatter', 
  mode = 'lines',
  name = 'DNP', 
  line = list(
    width = 2,
    color = 'rgb(68, 1, 84)')
  )%>%
add_trace(
  opacity = 0.5,
  x = ~density2$x,
  y = ~density2$y,
  name = 'Set', 
    line = list(
    dash = "dash",
    width = 2,
    color = 'rgb(33, 144, 140)')
  )%>%
layout(
      autosize = FALSE,
    width = 800, 
    height = 600,
  xaxis = list(
    nticks = 20,
    range = c(0,2000),
    title = 'Accurate Mass [Da]',
    showgrid = FALSE, 
    zeroline = FALSE, 
    automargin = TRUE,
    showticklabels = TRUE,
    titlefont = f2, 
    tickfont = f
    ),
    yaxis = list(
      title = "Density",
      showgrid = FALSE,
      showline = FALSE,
      zeroline = FALSE,
      automargin = TRUE,
      showticklabels = TRUE,
      titlefont = f2, 
      tickfont = f),
  legend = list(font=f, x = 1, y = 1)
  )
dens_plot
```

##Set vs DNP Chemical diversity
```{r}
Chemical_diversity_comparison <- Classes_DNP_cf4pie %>% 
  
plot_ly() %>%
  add_pie(
    data = Classes_DNP_cf4pie$Percent, 
    labels = Classes_DNP_cf4pie$Class_cf_DNP, 
    values = Classes_DNP_cf4pie$n,
    name = "DNP"
    ) %>%
  add_pie(
    data = Classes_cf4pie$Percent, 
    labels = Classes_cf4pie$Class_cf_STDS, 
    values = Classes_cf4pie$n,
    name = "Set", 
    domain = list(row = 1, column = 0)) %>% 
  layout(
    annotations = list(
      list(x = 1 , y = 1, font= f2, text = "DNP", showarrow = F, xref = 'paper', yref = 'paper'),
      list(x = 1 , y = 0, font = f2, text = "Set", showarrow = F, xref = 'paper', yref = 'paper')
      ),
    autosize = FALSE,
    width = 1000, 
    height = 900,
    margin = m,
    autosize = TRUE,
    showlegend = TRUE,
    grid = list(
      rows = 2, 
      columns = 1
      ),
    colorway = col_seq_12,
      #c("#440154FF", "#481769FF", "#472A7AFF", "#433D84FF", "#3D4E8AFF", "#355E8DFF" ,"#2E6D8EFF", "#297B8EFF", "#23898EFF", "#1F978BFF", "#21A585FF", "#2EB37CFF", "#46C06FFF", "#65CB5EFF", "#89D548FF", "#B0DD2FFF", "#D8E219FF", "#FDE725FF"),
    xaxis = list(
      showgrid = FALSE, 
      zeroline = TRUE, 
      automargin = TRUE,
      showticklabels = TRUE,
      titlefont = f2
      ),
    yaxis = list(
      showgrid = FALSE, 
      zeroline = TRUE, 
      automargin = TRUE,
      showticklabels = TRUE,
      titlefont = f2, 
      tickfont = f
    ),
font = f,
    legend =  list(
      font = f
      #orientation = 'h'
      )
)

Chemical_diversity_comparison
```

##Set Biological Families
```{r}
Families_in_set_2 <- Plotting_Families_3 %>%
  
plot_ly() %>%
  
add_trace(x = ~Names_List_Families, name =~Kingdom_cof_DNP, 
          y = ~as.numeric.Counts_List_Families., 
          color = (~Kingdom_cof_DNP),
          name = "", alpha = 1, type = "bar",
          text = paste(Plotting_Families_3[,"as.numeric.Counts_List_Families."]),
          textposition = 'auto',
          textfont = w,
          colors = c("#440154FF", 
                     "#FDE725FF",
                     "#21908CFF"
                     )
          ) %>%  
  
layout(autosize = FALSE,    width = 1200, 
    height = 900,
    barmode = "stacked",
       xaxis = list(
         autorange = TRUE, 
         showgrid = FALSE, 
         zeroline = TRUE, 
         automargin = TRUE,
         showticklabels = TRUE,
         titlefont = f2, 
         tickfont = f,
         tickangle = 300,
         title = "Family"),
       yaxis = list(
         showgrid = FALSE, 
         zeroline = FALSE, 
         automargin = TRUE,
         showticklabels = TRUE,
         titlefont = f2, 
         tickfont = f, 
         title = "Counts"
         ),
       legend = list(font = f2, x = 0.8, y = 0.9)

       )

Families_in_set_2
```

##MS instruments
```{r}
colourCount = length(unique(STDS_tax$lib_val_STDS))
getPalette = colorRampPalette(brewer.pal(14, "Paired"))

order1 <- ggplot(data = STDS_tax) +
  geom_mosaic(aes(x = product(MS_source_type), fill=(lib_val_STDS)), na.rm=TRUE) +
  labs(x = "Instrument sources") +
  theme(plot.title = element_text(size = rel(24))) +
  scale_fill_manual(name = "Library", values = getPalette(colourCount)) +
  # scale_fill_viridis(discrete=TRUE) +
  # scale_fill_jco() +
  theme(legend.title = element_text(color = "black", size = 16, family = "Helvetica"),
        legend.text = element_text(color = "black", size = 12, family = "Helvetica"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_blank(),
        axis.title.x = element_text(color = "black", size = 16, family = "Helvetica"),
        axis.text.x = element_text(color = "black", size = 12, family = "Helvetica"),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()
        )

ms <- ggplotly(order1)

ms
```

##F1 scores
```{r}
F1 <- F1_scores %>%
plot_ly() %>%
add_trace(x = F1_scores$Tool, 
          y = F1_scores$F1_scores_unweighted, 
          marker = list(color = 'rgb(68, 1, 84)'),
          name = "Initial", alpha = 1, type = "bar",
          text = paste(round(F1_scores$F1_scores_unweighted, digits = 1)),
          textposition = 'auto',
          textfont = w
          )%>%
add_trace(x = F1_scores$Tool,
          y = F1_scores$F1_scores_weighted, 
          marker = list(color = 'rgb(33, 144, 140)'),
          name = "Weighted", alpha = 1, type = "bar",
          text = paste(round(F1_scores$F1_scores_weighted, digits = 1)),
          textposition = 'auto',
          textfont = w
          )%>%
layout(barmode = "group",
       xaxis = list(
         showgrid = FALSE, 
         zeroline = FALSE, 
         title = FALSE, 
         titlefont = f2, 
         tickfont = f
         ),
       yaxis = list(
         showgrid = FALSE,
         zeroline = FALSE, 
         title = "F1 score [%]", 
         titlefont = f,
         tickfont = f,
         range = c(0,100)
         ),
       legend = list(
         font = f
         )
)

F1
```

##Venn
###initial
```{r}
v_initial <- euler(Venn_initial, 
           input="union", 
           shape="ellipse")

v1 <- plot(v_initial,
           legend = TRUE,
           fills = c("#21908CFF", "#440154FF", "#FDE725FF"), 
           alpha = 0.8,
           edges = FALSE,
           labels = FALSE,
           quantities = l2
           )
v1
```

```{r eval=FALSE, include=FALSE}
pdf("6_Venn_initial.pdf")

v_initial <- euler(Venn_initial, 
           input="union", 
           shape="ellipse")

v1 <- plot(v_initial,
           legend = TRUE,
           fills = c("#21908CFF", "#440154FF", "#FDE725FF"), 
           alpha = 0.8,
           edges = FALSE,
           labels = FALSE,
           quantities = l2
           )
v1

# Close the PDF file's associated graphics device (necessary to finalize the output)
dev.off()
```

###weighted
```{r}
v <- euler(Venn, 
           input = "union", 
           shape = "ellipse"
                   )
v2 <- plot(v,
          legend = TRUE,
          fills = c("#21908CFF", "#440154FF", "#FDE725FF"), 
          alpha=0.8,
          edges = FALSE,
          labels = FALSE,
          quantities = l2
          )
v2
```

```{r eval=FALSE, include=FALSE}
pdf("7_Venn_weighted.pdf")

v <- euler(Venn, 
           input = "union", 
           shape = "ellipse"
                   )
v2 <- plot(v,
          legend = TRUE,
          fills = c("#21908CFF", "#440154FF", "#FDE725FF"), 
          alpha=0.8,
          edges = FALSE,
          labels = FALSE,
          quantities = l2
          )
v2

# Close the PDF file's associated graphics device (necessary to finalize the output)
dev.off()
```

##ROC
```{r}
roc <- plot_ly(ROC, x = ~ x) %>%
  add_trace(
    y = ~ISDB, 
    name = 'ISDB',
    line = list(
      shape = "hv", 
      color = "#FDE725FF"
      ),
    marker = list(
      size = 0,
      opacity = 0
      )
    )%>%
  add_trace(
    y = ~ ISDB_Weighted, 
    name = 'ISDB Weighted', 
    line = list(
      shape = "hv",
      color = "#FDE725FF", 
      dash = 'dash'
      ), 
    marker = list(
      size = 0, 
      opacity = 0
      )
    ) %>%
  add_trace(
    y = ~ Sirius,
    name = 'Sirius', 
    line = list(
      shape = "hv",
      color = "#21908CFF"
      ),
    marker = list(
      size = 0, 
      opacity = 0
      )
    ) %>%
  add_trace(
    y = ~ Sirius_Weighted,
    name = 'Sirius Weighted', 
    line = list(
      shape = "hv",
      color = "#21908CFF",
      dash = 'dash'
      ), 
    marker = list(
      size = 0,
      opacity = 0
      )
    ) %>%
  add_trace(
    y = ~ MSFinder,
    name = 'MSFinder',
    line = list(
      shape = "hv",
      color = "#440154FF"
      ),
    marker = list(
      size = 0,
      opacity = 0
      )
    ) %>%
  add_trace(
    y = ~ MSFinder_Weighted,
    name = 'MSFinder Weighted', 
    line = list(
      shape = "hv", 
      color = "#440154FF", 
      dash = 'dash'
      ), 
    marker = list(
      size = 0,
      opacity = 0
      )
    ) %>% 
  layout(
    autosize = FALSE,
    width = 900, 
    height = 500,
    margin = m,
    colorway = c("#C0C0C0"),
    barmode = "stack",
    xaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      title = "Rank", 
      titlefont = f2,
      tickfont = f, 
      range = c(0,500),  
      automargin = TRUE
      ),
    yaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      title = "Correct short IK annotations",
      titlefont = f2,
      tickfont = f,  
      automargin = TRUE
      ),
    legend = l,
    showmarker = F
    )

roc
```

##Optimization
###1
```{r}
o_1 <- plot_ly(x = Results_degraded_01_01$ScoreDT$score_fam, 
               y = Results_degraded_01_01$ScoreDT$score_gen, 
               z = Results_degraded_01_01$ScoreDT$score_sp, 
               color = Results_degraded_01_01$ScoreDT$Score,
               type = 'scatter3d', 
               mode = 'lines + markers',
               marker = list(
                 size = 4
                 )
               ) %>%

layout(scene = list(
         xaxis = list(
           title = 'fam',
           type = 'lin',
           zerolinewidth = 1,
           ticklen = 5,
           gridwidth = 2
           ),
         yaxis = list(
           title = 'gen',
           type = 'lin',
           zerolinewidth = 1,
           ticklen = 5,
           gridwith = 2
           ),
         zaxis = list(
           title = 'sp',
           type = 'lin',
           zerolinewidth = 1,
           ticklen = 5,
           gridwith = 2)
          )
       )
o_1
```

###2
```{r}
o_2 <- plot_ly(x = Results_degraded_02_01$ScoreDT$score_fam, 
               y = Results_degraded_02_01$ScoreDT$score_gen, 
               z = Results_degraded_02_01$ScoreDT$score_sp, 
               color = Results_degraded_02_01$ScoreDT$Score,
               type = 'scatter3d', 
               mode = 'lines + markers',
               marker = list(
                 size = 4
                 )
               ) %>%

layout(scene = list(
         xaxis = list(
           title = 'fam',
           type = 'lin',
           zerolinewidth = 1,
           ticklen = 5,
           gridwidth = 2
           ),
         yaxis = list(
           title = 'gen',
           type = 'lin',
           zerolinewidth = 1,
           ticklen = 5,
           gridwith = 2
           ),
         zaxis = list(
           title = 'sp',
           type = 'lin',
           zerolinewidth = 1,
           ticklen = 5,
           gridwith = 2)
          )
       )
o_2
```

###3
```{r}
o_3 <- plot_ly(x = Results_degraded_03_01$ScoreDT$score_fam, 
               y = Results_degraded_03_01$ScoreDT$score_gen, 
               z = Results_degraded_03_01$ScoreDT$score_sp, 
               color = Results_degraded_03_01$ScoreDT$Score,
               type = 'scatter3d', 
               mode = 'lines + markers',
               marker = list(
                 size = 4
                 )
               ) %>%

layout(scene = list(
         xaxis = list(
           title = 'fam',
           type = 'lin',
           zerolinewidth = 1,
           ticklen = 5,
           gridwidth = 2
           ),
         yaxis = list(
           title = 'gen',
           type = 'lin',
           zerolinewidth = 1,
           ticklen = 5,
           gridwith = 2
           ),
         zaxis = list(
           title = 'sp',
           type = 'lin',
           zerolinewidth = 1,
           ticklen = 5,
           gridwith = 2)
          )
       )
o_3
```

###4
```{r}
o_4 <- plot_ly(x = Results_degraded_04_01$ScoreDT$score_fam, 
               y = Results_degraded_04_01$ScoreDT$score_gen, 
               z = Results_degraded_04_01$ScoreDT$score_sp, 
               color = Results_degraded_04_01$ScoreDT$Score,
               type = 'scatter3d', 
               mode = 'lines + markers',
               marker = list(
                 size = 4
                 )
               ) %>%

layout(scene = list(
         xaxis = list(
           title = 'fam',
           type = 'lin',
           zerolinewidth = 1,
           ticklen = 5,
           gridwidth = 2
           ),
         yaxis = list(
           title = 'gen',
           type = 'lin',
           zerolinewidth = 1,
           ticklen = 5,
           gridwith = 2
           ),
         zaxis = list(
           title = 'sp',
           type = 'lin',
           zerolinewidth = 1,
           ticklen = 5,
           gridwith = 2)
          )
       )
o_4
```

##Suppl. Bias low/high masses
```{r}
Accurate_masses <- plot_ly(
  opacity = 0.6, 
  alpha = 0.6,
  type = 'box'
  ) %>%
add_trace(y = ~Identified$pepmass_val_STDS -1.007276, 
          name = "Identified"
          )%>%
add_trace(y = ~Non_Identified$pepmass_val_STDS -1.007276,
          name = "Non-Identified"
          )%>%
layout(
  colorway = c(
    '#C67383',
    '#73C6B6'
    ),
  xaxis = list(
    autorange = TRUE, 
    showgrid = FALSE,
    zeroline = FALSE,
    titlefont = f2,
    tickfont = f
    ),
  yaxis = list(
    autorange = TRUE, 
    showgrid = FALSE, 
    zeroline = FALSE,
    title = "Accurate mass [Da]",
    titlefont = f, 
    tickfont = f
    ),
  legend = l
  )

Accurate_masses
```

```{r}
summary(Identified$pepmass_val_STDS)
summary(Non_Identified$pepmass_val_STDS)
```

#Export
##ORCA_PDF
```{r eval=FALSE, include=FALSE}
Sys.setenv('MAPBOX_TOKEN' = 'sk.eyJ1IjoiYWRhZmVkZSIsImEiOiJjanNwcnExNWwwNWVwNDRudDM2amJzb2htIn0.-qqOsWXic14b5Yxj1oPPlw')
orca(dens_plot, "1.svg")
orca(Chemical_diversity_comparison, "2.svg")
orca(Families_in_set_2, "3.svg")
orca(ms, "4.svg")
orca(F1, "5.svg")
orca(roc, "8.svg")
orca(Accurate_masses, "9.svg")
orca(o_1, "10.svg")
orca(o_2, "11.svg")
orca(o_3, "12.svg")
orca(o_4, "12.svg")
```

##html
```{r}
saveWidget(as_widget(dens_plot), "1.html")
saveWidget(as_widget(Chemical_diversity_comparison), "2.html")
saveWidget(as_widget(Families_in_set_2), "3.html")
saveWidget(as_widget(ms), "4.html")
saveWidget(as_widget(F1), "5.html")
saveWidget(as_widget(roc), "8.html")
saveWidget(as_widget(Accurate_masses), "9.html")
saveWidget(as_widget(o_1), "10.html")
saveWidget(as_widget(o_2), "11.html")
saveWidget(as_widget(o_3), "12.html")
saveWidget(as_widget(o_4), "13.html")
```